---
title: "Driving Experience"
author: William You
date: 21 June, 2018
output: 
  ioslides_presentation:
    css: 'C:/road_safety_ambition/driver experience/format.css'
widescreen: True

---

## Claim Frequency By Driver Experience{#drvexp}
<style> .image-wrapper p { margin-top: -50px; } #drvexp,#drvexp2,#age1,#age2,#expage,#expage2 { display: flex; }</style>

<div class="image-wrapper">
```{r drvexp, echo=FALSE,warning=FALSE,fig.align="left",fig.width=8,fig.height=6}
plotexp

```
</div>
<div >
- Driver's with less experience are more likely to claim than older drivers (~5%).
</div>

## Average Claim Cost By Driver Experience{#drvexp2}

<div class="image-wrapper">
```{r drvexp2, echo=FALSE,warning=FALSE,fig.align="left",fig.width=7,fig.height=6}

plotexp2

```
</div>

<div>
- The average cost of a claim for a driver with less experience is more (~12.5%) than a driver with more experience.

</div>

## Claim Frequency By Driver Age{#age1}

<div class="image-wrapper">

```{r age, echo=FALSE,warning=FALSE,fig.align="left",fig.width=7,fig.height=6}

plot1

```
</div>
- Younger drivers are more likely to make a claim than older drivers (~3%).

## Average Claim Cost By Driver Age{#age2}

<div class="image-wrapper">
```{r age2, echo=FALSE,warning=FALSE,fig.align="left",fig.width=7,fig.height=6}

plot2

```
</div>

- Average claims cost for younger drivers are much higher than older drivers (~12.5%).

## Claims Frequency By Driver Experience and Age{#expage}

<div class="image-wrapper">
```{r drvexp_age, echo=FALSE,warning=FALSE,fig.align="center",fig.width=6,fig.height=6}

plot_drvexp_age

```
</div>

## Average Claim Cost By Driver Experience and Age{#expage2}

<div class="image-wrapper">
```{r drvexp_age2, echo=FALSE,warning=FALSE,fig.align="center",fig.width=6,fig.height=6}

plot_drvexp_age_cs

```
</div>